Estimating the number of migrants based on kinship relationships

### 2021-05-21 latex/ms.tex
set all equations; close #4

\title{Estimating the number of migrants using between-population sibling pairs}%\protect\thanks{This is an example for title footnote.}}

@@

@@

\begin{align}
\widehat{m_3} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
\label{AP-4}
\end{align}

@@

\begin{align}
\widehat{M_5} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
\label{AP-6}
\end{align}

>>>>

\title{Estimating the number of migrants based on kinship relationships}%\protect\thanks{This is an example for title footnote.}}

@@

\begin{align}
\widehat{m_2} &= \frac{N_{2} \widetilde{H}_{\rm PO,bet} } {2 n_{\rm O, 1} n_{\rm P, 2} }
\label{PO-4}
\end{align}

@@

\begin{align}
\widehat{m_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
\label{AP-4}
\end{align}

@@

\begin{align}
\widehat{M_4} &=  \frac{ \left(\widetilde{H}_{\rm HS,bet} + \widetilde{H}_{\rm PO,bet}\right) \left(2 n_{\rm O, 1} n_{\rm P, 1} + 1\right) \left(2 n_{\rm O, 2} n_{\rm P, 2} + 1\right)} {2n_{\rm O, 1} \left(2 n_{\rm O, 2} + n_{\rm P, 2}\right) \left(\widetilde{H}_{\rm PO, 1} + 1\right) \left(\widetilde{H}_{\rm PO, 2} + 1\right)}
\label{AP-6}
\end{align}
